\papertitle

### 2013-02-05 manuscript.tex
more edits

>>>>

Our system combines both the sensing of the H$^2$Bird and the execution of the
desired headings to steer the robot towards the goal. The sensing is performed
on the ground station using frame differencing and a particle filter. The
H$^2$Bird steers to the heading directed by the ground station using a
quaternion-based PID controller.
